\begin{savequote}[15cm]
  \vspace{-30mm}
  \sffamily\raggedleft
  At all costs, avoid complexity. That rule is a life saver.
  \qauthor{A Seasoned Engineer.}
\end{savequote}
\chapter{Counting words made simple}

It is mandatory to include the word count of your thesis in the
information page. There are many constructs shown on the Internet but
we choose to go for the simplest solution possible.

\section{What to count}
It is resonable to only count the words in the report proper.
This implies only counting the words in the chapters, which is easy
enough by using the \texttt{texcount} command with a \define{glob} for the
chapters: \texttt{chapters/*.tex}

\section{How to count}
\begin{lstlisting}[language=sh]
texcount  -inc -sum  -1 chapters/*.tex > wordcount.txt
\end{lstlisting}

This file is then simply read inside the info block using \texttt{\textbackslash{}input}:
\begin{lstlisting}[language=TeX,emph={wordcount,txt},emphstyle={\colorbox{Yellow}},morekeywords={begin,end}]
\begin{infoblock}
  word count: & \input{wordcount.txt} words.
\end{infoblock}
\end{lstlisting}
in the \texttt{partials/informationpage.tex} file.

\section{When to count}
To make sure that the word count in the file is updated in the
whenever a chapter file changes, we use the Makefile.

In the Makefile we make the \texttt{wordcount.txt} file dependent on the
chapter files with this simple rule:

\begin{lstlisting}[language=make,showtabs]
wordcount.txt: chapters/*.tex
	texcount  -inc -sum  -1 chapters/*.tex > wordcount.txt
\end{lstlisting}

and make the main.pdf file dependent on the \texttt{wordcount.txt} file as
well.

When that does not work for you, maybe because you cannot or will not
use \texttt{make} in your environment, then execute the
\texttt{texcount} as given above in the terminal.

Even simpler, delete the \texttt{wordcount.txt} file and run pdflatex
on your main document again. That is arranged with the little bit of
\LaTeX{} code in the \texttt{configuration/thesis\_config.tex} file.
For that to work you need to run latex with the \texttt{-shell-escape} switch.

\begin{lstlisting}[language=TeX,emph={wordcount,txt},emphstyle={\colorbox{Yellow}},morekeywords={begin,end}]
\IfFileExists{wordcount.txt}{}{
  % not exists
  \immediate\write18{texcount -inc -sum -1 chapters/*.tex > wordcount.txt}
}

\end{lstlisting}



By the way, we have if you are on Windows: we have good experience
with git bash + make installed via chocolaty, so you might want to try
that too.
